---
title: "Data 605 - HW2"
author: "Avery Davidowitz"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

## Problem set 1

1 Show that $A^TA \ne AA^T$ in general. (Proof and demonstration.)

We can easily prove this by contradiction. Let us assume that $A^TA = AA^T$ for any matrix A and we will find that this introduces a contradiction.
Let $A = \left[\begin{array}{c}2\\3\\1\end{array}\right]$ which is 3x1,
then $A^T = \left[\begin{array}{ccc}2&3&1\end{array}\right]$ which is 1x3.
By the definition of matrix multiplication $A^TA$ will result in a 1x1 matrix and $AA^T$ will result in a 3x3 matrix. Therefore, they cannot be equal and we now have a contradiction. This proves that $A^TA \ne AA^T \hspace{2 mm} \forall A$

Demonstrating in R:

```{r}
A = matrix(c(2,3,1),
             3, byrow=TRUE)
A
t(A)
t(A) %*% A
A %*% t(A)
```

2 For a special type of square matrix A, we get AT A = AAT . Under what conditions
 could this be true? (Hint: The Identity matrix I is an example of such a matrix).
 
This would be true in general for a symmetric matrix where by definition $A=A^T$
 
## Problem set 2

Write an R function to factorize a square matrix A into LU or LDU, whichever you
prefer. You don’t have to worry about permuting rows of A and you can assume that A is less
than 5x5, if you need to hard-code any variables in your code.


```{r}
lu_decomp <- function (A) {
  ### returns the LU decomposition for a matrix A with an assumption 
  ### that no permutation matrix P is required 
  
  # check for square dimension
  n <- dim(A)
  if (n[1] != n[2]) stop("must be a square")
  n <- n[1]
  L <- diag(n)
  U <- A
  for(i in 2:n){ 
    for(j in 1:(i-1)){
      L[i,j] <- U[i,j] / U[j,j] #constants used to zero out the first column of A
      U[i,] <- U[i,] - L[i,j] * U[j,] #first row of U = zero out the first entry of rows below it
    }
  }
  return(list(L,U))
  }
```

```{r}
B <- matrix(c(1, 2, -7, -1, -1, 1, 2, 1, 5), 3)
lu <- lu_decomp(B)
lu
```

