---
title: "Data 605 - HW9"
author: "Avery Davidowitz"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
The price of one share of stock in the Pilsdorff Beer Company is given by $Y_n$ 
on the nth day of the year. Finn observes that the difference $X_n = Y_{n+1} - Y_n$
appear to be independent random variables with a common distribution having mean = 0 
and variance = 1/4. If $Y_1 = 100$, estimate the probability that $Y_{365}$ is:

If $S_n$ is the sum of the random variables then $S_{364}$ is the sum up to $Y_{365}$:
$S_{364} = (Y_{365} - Y_{364}) +$ ... $(Y_2 - Y_1)$
By elimination we have:
$S_{364} = (Y_{365} - Y_1)$
So instead of solving for $P(Y_{365})$ we can solve for the normal of $P(S_{364} + 100) \ge$ the required level
with a mean = 0 and variance = $n\sigma^2= 364/4 = 91$

a) 100

```{r}
1 - pnorm(0, mean = 0, sd = sqrt(91))
```

b) 110

```{r}
1 - pnorm(10, mean = 0, sd = sqrt(91))
```

c) 120

```{r}
1 - pnorm(20, mean = 0, sd = sqrt(91))
```


## Question 2
Calculate the expected value and variance of the binomial distribution using the moment
generating function

The moment generating function for the binomial distribution is:
$M(t) = ((1 – p) + pe^t)^n$

The first derivative is by the chain rule equal to:
M'(t) = $n(pe^t)((1 – p) + pe^t)^{n - 1}$

Likewise the second derivative is:
M’’(t) = $n(n - 1)(pe^t)^2[(1 – p) + pe^t]^{n - 2} + n(pe^t)[(1 – p) + pe^t]^{n - 1}$

The mean is M'(0) and the variance is M’’(0) – M’$(0)^2$ which implies that:
M'(0) = $n(pe^0)[(1 – p) + pe^0]^{n - 1} = np$
M’’(0) – M’$(0)^2 = n(n - 1)p^2 +np - (np)^2 = np(1 - p)$

## Question 3
Calculate the expected value and variance of the exponential distribution using the moment
generating function

The moment generating function for the exponential distribution is:
$M(t)=\frac{\lambda}{\lambda−t}$
M'(t) = $\frac{\lambda}{(\lambda−t)^2}$

M''(t) = $\frac{2\lambda}{(\lambda−t)^3}$
Therefore:
EV = M'(0) = $\frac{1}{\lambda}$
Var(X)=M''(0)− M'$(0)^2 = \frac{1}{λ^2}$
