---
title: "Data 605 - W12 HW"
author: "Avery Davidowitz"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Libraries

```{r}
library(tidyverse)
```

## Data

```{r}
df <- readr::read_csv(paste0(getwd(),"/who.csv"))
head(df)
```

## 1 
Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the
variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss
whether the assumptions of simple linear regression met.

```{r}
ggplot(data=df, aes(x=TotExp, y=LifeExp)) + geom_point()
```

```{r}
life_exp_lm <- lm(LifeExp ~ TotExp, data = df)
summary(life_exp_lm)
```

The R squared value of .25 is very low and indicates that the model does not explain the dependent variable well.

## 2
Raise life expectancy to the 4.6 power (i.e., LifeExp^4.6). Raise total expenditures to the 0.06
power (nearly a log transform, TotExp^.06). Plot LifeExp^4.6 as a function of TotExp^.06, and r
re-run the simple regression model using the transformed variables. Provide and interpret the F
statistics, R^2, standard error, and p-values. Which model is "better?"

```{r}
df2 <- df |> dplyr::mutate(LifeExp = LifeExp^4.6) |> dplyr::mutate(TotExp = TotExp^.06)
life_exp_lm2 <- lm(LifeExp ~ TotExp, data = df2)
summary(life_exp_lm2)
```


