---
title: "DATA 605 - HW 10"
author: "Avery Davidowitz"
date: "`r Sys.Date()`"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Import Libraries
```{r}
library(markovchain)
```

# Create Markov chains
The states of the chain represent how much money Smith currently has. The transition matrix represents the probabilities of the bets at a given state. States 0 and 8 are absorbing states with a P00 and P88 equal to 1. 
```{r}
#timid strat Markov chain object
statesNames_timid <- c("0","1","2","3","4","5","6","7","8")
mc_timid <- new("markovchain", transitionMatrix=matrix(c(1,0,0,0,0,0,0,0,0,
                                                         .6,0,.4,0,0,0,0,0,0,
                                                         0,.6,0,.4,0,0,0,0,0,
                                                         0,0,.6,0,.4,0,0,0,0,
                                                         0,0,0,.6,0,.4,0,0,0,
                                                         0,0,0,0,.6,0,.4,0,0,
                                                         0,0,0,0,0,.6,0,.4,0,
                                                         0,0,0,0,0,0,.6,0,.4,
                                                         0,0,0,0,0,0,0,0,1),byrow=TRUE,
nrow=9, dimnames=list(statesNames_timid,statesNames_timid)))
#bold strat Markov chain object
statesNames_bold <- c("0","1","2","4","8")
mc_bold <- new("markovchain", transitionMatrix=matrix(c(1,0,0,0,0,
                                                        .6,0,.4,0,0,
                                                        .6,0,0,.4,0,
                                                        .6,0,0,0,.4,
                                                         0,0,0,0,1),byrow=TRUE,
nrow=5, dimnames=list(statesNames_bold,statesNames_bold)))
```
## Absorbtion Probabilities
The absorption probabilities of the Markov chain ending in either state 0 or 8 represent the probability that the Smith will lose and stay in prison or win and escape.
```{r}
ap_timid <- absorptionProbabilities(mc_timid)
ap_bold <- absorptionProbabilities(mc_bold)
ap_timid
ap_bold
```
## Conclusion
As seen below if the prisoner Smith starts at 1 dollar and gambles using the bold strategy they are more likely to escape.
```{r}
# Question A)
ap_timid["1","8"]
# Question B)
ap_bold["1","8"]
# Question C)
ap_bold["1","8"] > ap_timid["1","8"]
```


