---
title: "Data 605 - DB13"
author: "Avery Davidowitz"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Libraries
```{r}
library(pracma)
```


## 4.3 Question 8

A rancher has 1000 feet of fending in which to construct adjacent, equally sized recatngular pens. What dimensions should these pens have to maximize the enclosed area?

Our fencing contraint yields:
3l + 2w = 1000

The cost function to optimize is:
area = l * w

Using substitution:
area = l * (1000 - 3l)/2

Calculate the derivative:
```{r}
area = expression(-3/2 * l^2 + 500*l)
deriv <- D(area, "l")
deriv
```
Using bisection to find the root for where deriv = 0

```{r}
root <- bisect(function(l) -3/2 * (2 * l) + 500, 0, 1000)
root
```

The optimal length is equal to:
```{r}
l <- root$root
l
```

The resulting maximized area is:

```{r}
fence_area <- function(l) {
  -3/2 * l^2 + 500*l
}
fence_area(l)
```

The optimal width is equal to:
```{r}
w <- fence_area(l)/l
w
```



