---
title: "Data 605 - HW13"
author: "Avery Davidowitz"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Import Libraries
```{r}
library(tidyverse)
library(pracma)
```


## Question 1
Use integration by substitution to solve the integral below.
$\int 4  e^{-7x} dx$
We will substitute $u = -7x$ differentiating both sides gives $du = -7 dx$ or the algebraic equivalent of $dx = \frac{du}{-7}$. Now we integrate with respect to du and then resubstitute $u = -7x$.

$$
\int4   \frac{e^{u} du}{-7} = \frac{-4}{7}\int e^{u} du = \frac{-4}{7}e^{u} = \frac{-4}{7}e^{-7x}
$$


## Question 2
Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of:
$\frac{dN}{dt} = -\frac{3150}{t^4} - 220$
bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a
function N(t) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.
$$\frac{dN}{dt} = -\frac{3150}{t^4} - 220$$ multiply both sides by dt
$$dN = -\frac{3150}{t^4}dt - 220dt$$ then integrate both sides
$$N(t) = -\frac{1050}{t^3} - 220t + C$$ Substituting in for N(1) = 6530
$$6530 = -1050 - 220 + C$$ Solving for C gives C = 7800 and yields or original function N(t):
$$N(t) = -\frac{1050}{t^3} - 220t + 7800$$

## Question 3
Find the total area of the red rectangles in the figure below, where the equation of the line is f(x) = 2x - 9.

The total area is equal to the sum of the area for each rectangle. Each is 1 wide.
The centers of the rectangles are at x= 5, 6, 7, 8 so the height of each rectangle is give by f(x).

```{r}
f <- function(x){
  2 * x - 9
}
area = (1 * f(5)) + (1 * f(6)) + (1 * f(7)) + (1 * f(8))
area
```

## Question 4
Find the area of the region bounded by the graphs of the given equations.
$f(x) = x^2 - 2x - 2$ , g(x) = x + 2
```{r}
ggplot(data.frame(x = c(-2,5)), aes(x=x)) +
  stat_function(fun= function(x){x^2 - 2*x - 2}, color = "blue") +
  stat_function(fun= function(x){x + 2}, color = "green")
```
Since the g(x) is greater than f(x) through the interval [-1, 4], the area bounded by the curves is given by:
$\int_{a}^{b} g(x)-f(x) \,dx$ then our area is given by: $\int_{-1}^{4}-x^2 + 3x + 4$
The integral is equal to $\frac{-x^3}{3}+3\frac{x^2}{2}+4x$ and evaluated between 4 and -1 gives:
```{r}
f <- function(x){
  -1/3 * x^3 + 3/2 * x^2 + 4 * x
}
area = f(4) - f(-1)
area
```

## Question 5
A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year.
There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize
inventory costs.

cost = 8.25 * orders + 3.75 * 110/orders
```{r}
ggplot(data.frame(x = c(0,20)), aes(x=x)) +
  stat_function(fun= function(x){8.25*x + (3.75 * 110)/x}, color = "blue")

cost <- function(x){
  8.25*x + (3.75 * 110)/x
}
cost_deriv <- function(x){
  8.25 - (3.75 * 110) * x^(-2)
}
#using the bisection method to find the root
root <- bisect(cost_deriv, 0, 15)
root
#since the root is not an integer we need to evaluate at the closest integer and choose the lower cost
cost(7)
cost(8)
```
7 orders minimizes inventory costs.

## Question 6
Use integration by parts to solve the integral below.
$\int ln( 9x ) * x^6 dx$

Integration by parts formula:
$$\int u dv = uv - \int vdu$$
If we set u = ln(9x) and $dv = x^6$ then:
$$\int ln( 9x ) * x^6 dx = ln(9x) * \frac{x^7}{7} - \int \frac{x^7}{7x} = ln(9x) * \frac{x^7}{7} - \frac{x^7}{49} + C$$

## Question 7
Determine whether f(x) is a probability density function on the interval 1, $e^6$ . If not, determine the value of the
definite integral.
$f(x) = \frac{1}{6x}$

```{r}
integrate(function(x) {1/(6*x)}, lower=1, upper=exp(6))
```
This is a probability density function over the interval because the area under the curve sums to 1.


