---
title: "Data607 HW7"
author: "Avery Davidowitz"
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
1. Let X1, X2, . . . , Xn be n mutually independent random variables, each of
which is uniformly distributed on the integers from 1 to k. Let Y denote the
minimum of the Xi’s. Find the distribution of Y 

## Question 2
2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).
This machine has a manufacturer’s expected lifetime of 10 years. This means
that we expect one failure every ten years. (Include the probability statements
and R Code for each part.)

a. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a geometric. (Hint: the probability is
equivalent to not failing during the first 8 years..
```{r}
p <- 1/10
ev <- 1/p
s_d <- sqrt((1 - p)/(p ^ 2))
p_8 <- ((1-p)^(8-1))*p
p
ev
s_d
p_8
```

b. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as an exponential
```{r}
lam <-1/10
ev <- 1/lam
s_d <- sqrt(1/lam^2)
pexp(8, lam, lower.tail = FALSE)
ev
s_d
```

c. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8
years
```{r}
p <- 1/10
ev <- 8*p
s_d <- sqrt(8 * p * (1-p))
pbinom(0, 8, p, lower.tail = TRUE)
ev
s_d
```

d. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a Poisson
```{r}
ev <- 1/10
s_d <- sqrt(ev)
pois_1 <- ppois(0, ev, lower.tail = TRUE)
pois_1^8
ev
s_d
```

